%%%%
% -- Instrument Description
% --     FOBOS Keck White Paper 2019
%%%%


\section{Recent and Ongoing Progress}
\label{sec:progress}

FOBOS development over the past year has focused on (1) engaging the
scientific and instrumentalist communities in discussions about the
FOBOS design, particularly with regard to science cases and
instrument feasibility, (2) initial development of an instrument
simulator and exposure-time calculator, (3) advancing the
optomechanical designs of the focal-plane and ADC systems, (4)
consolidating development of Fiber-WFOS for TMT and repurposing much
of the design for FOBOS at Keck, (5) working with Keck instrument
scientists and engineers toward a practical integration plan, and (6)
developing a detailed project execution plan, schedule, and budget.
Many of these activities were enabled by funds provided in response
to our previous white-paper submission.

Visits to Keck-user institutes have been particularly helpful in
building interest around the instrument and refining its
specifications. As of this writing, Bundy, MacDonald, and/or Westfall
have visited UCR (also joined by Michael Cooper from UCI), UCLA, Keck
observatory, LBNL, and UCSB. We plan to continue these visits, hoping
to visit UCB, UCD, and CIT before the end of the year.

Three specific ways the instrument conceptual design has been
affected by these conversations are the emphasis on the flexibility
of the focal-plane sampling, the ``first-light'' multiplex capacity,
and sensitivity toward the UV. Although the capabilities of PFS are a
common comparison for FOBOS, many of the science goals now enumerated
in Section 1 require target densities and/or wavelength coverage that
PFS will not provide; in the overlapping wavelength range between the
two instruments, FOBOS's survey speed is \comment{x} times larger
than PFS's. Given both this and the SSC's own assessment of the need
for multiplex at Keck, our current design includes 1800 single-fiber
apertures over a 17' FOV (our goal remains to access the full 20'
FOV), yeilding a target density of $\sim$8 arcmin$^{-2}$
(approximately the target density of DEEP2), but able to meet a
maximum target density of $\sim$30 arcmin$^{-2}$ in patches of the
focal-plane given the flexibility of the Starbugs positioning system.
Although this mode is our first-light capability, a strong message
from Keck users was that a large-format monolithic IFU and many
deployable IFUs were both highly desirable. Again, this makes
Starbugs attractive because other fiber-positioning systems (e.g.,
robotic or Echidna-like zonal positioners) would make swapping
focal-plane formats much more difficult or untenable \comment{check
this}. Our initial concepts for these different focal-plane formats
provided a secondary motivation for FOBOS's large pseudo-slit
capacity: it can yield a monolithic IFU with a FOV comparable to
VLT/MUSE and provided 15-100 smaller deployable IFUs. Finally, Keck
remains unique in its throughput toward the atmospheric limit. No
other current or planned \comment{check this again} spectrograph for
10m-class telescopes provides sensitivity below $\sim$380nm,
providing FOBOS with a unique capability among the landscape of
forthcoming instrumentation.

An identified risk of the front-end design of FOBOS is in the
coupling of the microlens fore-optics to the fiber and the coupling
of the microlens entrance aperture with the Keck II focal plane. It
is critical that both of these couplings minimize losses. Using funds
provided by a UCO mini-grant, we will address and begin to mitigate
these risks via prototype fiber builds that are tested in the fiber
labs at UCO and LBL \comment{confirm that} and perform on-sky tests
that verify the lab results. Lab tests have already begin with
imaging the near- and far-field input and/or output beams of bare
fibers. We have optomechanical designs of the microlens-fiber
coupling, and have ordered hardware to be begin fabrication. We plan
to propose for experiments to be performed during engineering time at
Keck by the end of the year \comment{check this}.

Finally, with the permission of the SSC, we proposed for
instrument-design funds from the NSF via its new Mid-scale Research
Infrastructure scheme. Although the proposal was ultimately
unsuccessful, preparation of the proposal led to a ground swell of
development in our project planning and science development, much of
which is included in this submission.
